---
title: "OzFlux NEE SAM Modelling"
author: "Jon Page"
date: "24/07/2020"
Last Updated: date()
output: github_document
---

This notebook is to document my modelling of OzFlux sites using a replication of Liu et al's model from their 2019 paper.

I have downloaded the model code from github (https://github.com/yliu11/NEE_Bayes_model, accessed 15/06/20).

I need to coerce data into the required input formats and produce a wrapper script.

Let's activate!

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

## Working on Howard Springs and Sturt Plains

I will first attempt to replicate the modelling at one site, Sturt Plains.

```{r Site Selection, include=FALSE}
Site = "DryRiver"
```

I need to access the full fluxnet data for this, as the data I have from previous modelling of this site does not include SWC. Daily FluxNet data will be used.


```{r Input Data}
if (file.exists(paste0(Site,"_Input_NDVI.Rdata"))){
  message("Gosh! Processed daily OzFlux data already exists for ",Site)
} else {
  source("OzFluxProcess_NDVI.R")
  OzFluxProcess(Site)
}
```

We have extracted the necessary data from the FluxNet and NDVI files. We can now test-run the model:

```{r Run Model, eval = FALSE}

library(R2jags)

# Load the input data
load(paste0(Site,"_Input.Rdata"))
# Assign to standard name
Data = eval(as.name(paste0(Site,"_Input")))

   # Define the parameters for the model operation
   # samples to be kept after burn in
   samples = 50000
   # iterations for burn in
   burn = samples * 0.1 
   # number of iterations where samplers adapt behaviour to maximise efficiency
   nadapt = 100  
   # The number of MCMC chains to run
   nchains = 4 
   # thinning rate
   # save every thin-th iteration to reduce correlation between 
   # consecutive values in the chain
   thin = 10 
   
    # Parameters to save
    parameters = c("NEE","muNEE")

   jags = jags(model.file='Model.R', data=Data, n.chains=nchains, parameters.to.save = parameters) 
```


This works and so we take it onto the storm servers for the greater power.

## NIRV or NDVI?

The first model runs were performed using NIRV data. This has a much smaller range than NDVI but correlates well. The SAM and AR(1) models produce similar R2 values for HS and SP as those reported in Yao's paper. However, the current-only model has much higher R2 than Yao found. I have not yet identified why this is, but have become intrigued by the Veg Index used and its implications.

I have rerun the gap-filling from Sami, but this time for NDVI. Note that both NIRV and NDVI have exactly the same gaps in the data.

We are also gap-filling 40% of the data!!!! This seems excessive but may not be. The longest run of missing data is 73 days, with 1237 gaps. The median is 3 days and the mean is 4.9 days. The mean run of data is 7.1 days and the median is 2. 

```{r NDVI vs NIRV and gapfilling}
load("VegIndex_NDVI.Rdata")
NDVI = VegIndex
load("VegIndex.Rdata")
NIRV = VegIndex

ndvi.na = rle(is.na(NDVI$ndvi))
max(ndvi.na$lengths[ndvi.na$values==TRUE])

nirv.na = rle(is.na(NIRV$nirv))
max(nirv.na$lengths[nirv.na$values==TRUE])

sum(is.na(NDVI$ndvi))/length(NDVI$ndvi)
```

I will rerun the model with this data instead of the NIRV data and see if there is any difference in the model results.

## Identified Issues

I was using the daily sums of NEE and SWR - these have been changed to mean.

Soil moisture values are also interesting and quite different. Sturt Plains in particular has some problematic values in the later years.

The time windows are also different between my work and Yao's.

| | Yao | Me |
|:-:|:-:|:-:|
| HS | 24/07/01 - 31/12/14 | 01/01/03 - 01/01/18 |
| SP | 14/08/08 - 31/12/14 | 01/01/09 - 01/01/18 |

I was also using a possibly incorrect way of calculating the climatic inputs. I was using VPD in kPa rather than hPa and SWC as a decimal rather than percentage. Additionally I was mean centreing PPT at a different stage which resulted in an additive shift of values. 
However, I re-ran the model for Sturt Plains with an input using the above differences and got the same R2 values - as such, as expected, these scale issues aren't a factor in the difference between Yao and I. 
Further, in investigating this, I checked the FluxNet files for Aus sites, and the input values are (to the eye) the same. The issue now either lies in my implementation of the model or with the differing time periods. 

I am checking the time periods using Sturt Plains again by cutting off my input file at 31/12/14 - unfortunately I cannot add data to the start of my series!